
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{academicons}
\usepackage[T1]{fontenc}
\usepackage[pdfencoding=auto]{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemNoColon}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemNoColonNB}[1]{
  \item[]\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoColon}[2]{\resumeItemNoColon{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubheadingNoColon}[2]{
  \vspace{-1pt}\small \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}


\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pdfstringdefDisableCommands{%
  \def\faGraduationCap{\unichar{"F19D}}
  \def\faFlask{\unichar{"F0C3}}
  \def\aiGoogleScholar{\unichar{"E9D4}}
  \def\faPieChart{\unichar{"F200}}
  \def\faGears{\unichar{"F085}}
  \def\faClipboard{\unichar{"F0EA}}
  \def\faBriefcase{\unichar{"F0B1}}
  %
}


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	 \textbf{{\Large Amanpreet Singh}} & \\
     
     \href{mailto:amanpreet.singh@stonybrook.edu}{\faEnvelope \space amanpreet.singh@stonybrook.edu} & \href{https://www.linkedin.com/in/amanpreet-singh-k}{\faLinkedin \space /amanpreet-singh-k}\\
       \faPhone \space +1 631-312-2565 & \href{https://github.com/amanpreet692}{\faGithub \space /amanpreet692}\\
\end{tabular*}

%-----------EDUCATION-----------------
\section {{\faGraduationCap} Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {Master's in Computer Science; GPA: 3.97}{2019 -- 2021}
      \resumeItemListStart
       \resumeItem{Thesis}
       {Sequence Labeling for Network File System Specifications\\
       \textbf{Advised by:}
       {Prof. Niranjan Balasubramanian}}
      \resumeItem{Courses}
       {Natural Language Processing, Machine Learning, Data Science, Probability \& Statistics}
       \resumeItemListEnd
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Information Technology;  First Class with Distinction (72.9\%)}{2011 -- 2015}
      \resumeItemListStart
      \resumeItem{Courses}
       {Data Structures \& Algorithms, Artificial Intelligence, Discrete Mathematics, Databases}
       \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PUBLICATION(S)-----------------
\section{{\aiGoogleScholar}Publications}
  \resumeSubHeadingListStart
    \item\small
    {\textbf{Singh, A.}, \& Balasubramanian, N. (2020), ``Open4Business (O4B): An Open Access Dataset for Summarizing Business Documents'', \textit{Workshop on Dataset Curation and Security - NeurIPS 2020}}\vspace{-2pt}
    \item\small
      {Nayak, A., Acharya, N., \textbf{Singh, A.}, Sakhapara, A., \& Geleda, B.(2015),  ``Visualization of Mechanics Problems based on Natural Language Processing'', \textit{International Journal of Computer Applications}, 116(14)}\vspace{-2pt}
      
\resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{{\faFlask} Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{NER for system specifications}
    {Dataset annotation using Brat and code sequence classification in network file system specification documents by fine-tuning pre-trained language models. The language model itself is first fine-tuned on a manually scraped corpus for better domain adaptability. The lack of a large training set for the end task is a challenge.}
   \resumeSubItem{Startup Acquisition Prediction}
    {Implementation and evaluation of different ensemble methods including anomaly detection, Naive Bayes and random forest on highly imbalanced data to predict whether a startup will be acquired.}
  \resumeSubItem{Toxic Online Comments} {Multi-label toxicity detection in Wikipedia Comments and transfer learning effectiveness of the classifier on Twitter dataset. Analyzed the results of stacked LSTM/GRU against BERT and distilBERT models.}
    \resumeSubItem{Long Documents Classification}
    {Parsing and multi-class categorization of documents with over 10k tokens using Bag of words, Tf-Idf, Doc2Vec and Attention based Neural models.}
   \resumeSubItem{Chess Player Ratings} {
     Predicting the Elo rating of a chess player from the moves sequence. Efforts involved EDA and feature engineering using Pandas and Matplotlib; as well as modeling with Linear Regression and Random Forest.}
  \resumeSubItem{Physual}
      {A text to scene generation system to visualize Physics problems with Stanford NLP, Java3D and Blender.}
 
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{{\faBriefcase} Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {SS\&C Intralinks}{Waltham, MA}
      {Machine Learning Engineer Intern (NLP)}{May 2020 -- Dec 2020}
       \resumeItemListStart
      \resumeItem{Abstractive Summarization}
       {Deep learning and REST service based business document summarizer:\\
       1. Curated and published a dataset of 18k open access business articles with their abstracts as summaries.\\
       2. Improved ROUGE score of SOTA models like BART and T5 by more than 10 points via fine-tuning.\\
       3. Built a custom encoder-decoder for T5 model to compress large inputs and avoid memory constraints.\\
       4. Adapted existing seq2seq model to ONNX quantization format reducing size by 75\% and inference time by 30\%.
       5. Flask based service to return raw abstractive summary with highlighted essential parts of a PDF. 
       }
       \resumeItemListEnd
     \resumeSubheading
      {J.P. Morgan Chase \& Co.}{Mumbai, India}
      {Senior Software Development Engineer}{Feb 2018 -- Aug 2019}
      \resumeItemListStart
      \resumeItem{NLP Query Service}
       {An interactive system to resolve user queries that uses a model trained on the CRF classifier from StanfordCore NLP and returns the nearest possible solution from an existing knowledge base.}
       \resumeItem{Trader Analytics} 
       {Introduced statistical enhancements in the core application such as absolute and percent variance, market share and standard deviation of historical stock prices to aid in trading decisions.}
       \resumeItem{Real-Time Pricing}
          {Developed a component using Spring, JMS and TDD principles that approximates real-time market risk using live prices; and publishes out the result. It helped retire a legacy system saving the firm $\sim$\$250k.}
       \resumeItemListEnd
       \pagebreak
      \vspace{-3pt}\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \\\textit{\small Software Development Engineer} & \textit{\small July 2015 -- Jan 2018}
      \end{tabular*}\vspace{-5pt}
       \resumeItemListStart
      \resumeItem{Risk Management System}
          {Worked extensively on the core app used by traders for visualizing and hedging risk;\\
          1. Optimized the data feed using LMax Disruptor, a low latency Java queue for upto 20\% faster trades processing.\\
          2. Framework to validate critical live market data results which reduced manual testing effort by 90\%.\\
          3. Mechanism to switch from a MongoDB replica set to standalone instance in the event of a data center failure.}  
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%--------TECHNICAL SKILLS------------
\section{{\faGears} Technical Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{Languages}{Python, Java, Unix Shell Scripting, SQL, MATLAB}
 \resumeSubItem{Frameworks}{PyTorch, TensorFlow, HuggingFace(Contributor), Pandas, NumPy, Scikit-Learn, Spring, Swagger}
 \resumeSubItem{Databases}{Sybase ASE, MongoDB, MySQL}
 \resumeSubHeadingListEnd
 
 
 %--------TEACHING EXPERIENCE------------
\section{{\faClipboard} Teaching}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {Teaching Assistant}{Aug 2019 -- May 2020}
\begin{enumerate}[label={}, labelsep=0pt, leftmargin=0pt]
    \item CSE 214 Data Structures in Java
    \item CSE 354 Natural Language Processing
    \item CSE 416 Software Engineering
\end{enumerate}
      
\resumeSubheading
      {K.J. Somaiya College of Engineering}{Mumbai, India}
      {Guest Lecturer}{Mar 2019}
\begin{enumerate}[label={}, labelsep=0pt, leftmargin=0pt]
    \item Seminar on benefits of using Spring and SpringBoot frameworks for client-server apps for undergrad juniors.
\end{enumerate}

\resumeSubheading
      {CrossNibble Technologies}{Mumbai, India}
      {Technical Instructor}{Mar 2015 -- July 2015}
      
\begin{enumerate}[label={}, labelsep=0pt, leftmargin=0pt]
    \item Course Designer and instructor for hands-on Java programming for a class of 25 undergrads.
\end{enumerate}

\resumeSubHeadingListEnd
\end{document}