
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{academicons}
\usepackage[T1]{fontenc}

\usepackage[pdfencoding=auto]{hyperref}

\pdfstringdefDisableCommands{%
  \def\faGraduationCap{\unichar{"F19D}}
  \def\faFlask{\unichar{"F0C3}}
  \def\aiGoogleScholar{\unichar{"E9D4}}
  \def\faPieChart{\unichar{"F200}}
  \def\faGears{\unichar{"F085}}
  %
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemNoColon}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoColon}[2]{\resumeItemNoColon{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	 \textbf{{\Large Amanpreet Singh}} &
     \href{mailto:amanpreet.singh@stonybrook.edu}{\faEnvelope \space amanpreet.singh@stonybrook.edu}\\
     \faPhone \space +1 631-312-2565 &
     \href{https://www.linkedin.com/in/amanpreet-singh-k}{\faLinkedin \space /amanpreet-singh-k}\\
\end{tabular*}

%-----------EDUCATION-----------------
\section {{\faGraduationCap} Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Stony Brook University}{New York, U.S.A.}
      {Master of Science in Computer Science; GPA: 3.93}{2019 -- 2021}
      \resumeItemListStart
      \resumeItem{Courses}
       {Analysis of Algorithms, Natural Language Processing, Data Science, Probability \& Statistics}
       \resumeItem{Teaching Assistant}
       {CSE 354 - Natural Language Processing, CSE 416 - Software Engineering}
       \resumeItemListEnd
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Information Technology;  First Class with Distinction (72.9\%)}{2011 -- 2015}
      \resumeItemListStart
      \resumeItem{Courses}
       {Data Structures, Artificial Intelligence, Discrete Mathematics, Databases}
       \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{{\faPieChart} Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {J.P. Morgan Chase \& Co.}{Mumbai, India}
      {Senior Application Developer}{Feb 2018 -- Aug 2019}
      \resumeItemListStart
       \resumeItem{NLP Query Service}
       {An interactive system to resolve user queries that uses a model trained on the CRF classifier from StanfordCore NLP and returns the nearest possible solution from an existing knowledge base.}
       \resumeItem{Trader Analytics} 
       {Introduced statistical enhancements in the core application such as absolute and percent variance, market share and standard deviation of historical stock prices to aid in trading decisions.}
       \resumeItem{Memory Optimization}
       {Application heap usage profiling and G1 Garbage Collection tuning through careful analysis of humongous allocations resulting in 80\% fewer memory related issues.}
       \resumeItem{Real-Time Pricing}
          {Developed a component using Spring, REST, JMS and TDD principles that approximates real-time risk using live prices; and publishes them out. It helped retire a legacy system saving the firm $\sim$\$250k.}
	   \resumeItemListEnd
      \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \textit{\small Application Developer} & \textit{\small July 2015 -- Jan 2018} \\
      \end{tabular*}\vspace{-5pt}
      \resumeItemListStart
           \resumeItem{Risk Management System}
          {Worked extensively on the core app used by traders for visualizing and hedging risk;\\
          1. Optimized the data feed using LMax Disruptor, a low latency Java queue for upto 20\% faster processing.\\
          2. Process startup time improvement by 50\% through the use of Multi-threading and Spring annotations.\\
          }
          
       \resumeItem{Position/Trades feed migration:} {Spearheaded the development effort in migrating the critical source feeds and fixed several timely bugs reducing the reputational and operational risk.}
        \resumeItem{Market Data Source}
          {Framework for validating the functionality of a critical market data publishing app and reporting results using Java MXBeans and Apache POI. Reduced the manual testing effort by 90\%.}
          \resumeItem{MongoDB High availability}
          {Team point of contact for MongoDB. Built a mechanism to switch from replica set to standalone instance on the fly in case of a data center failure ensuring business continuity.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
  
%-----------PROJECTS-----------------
\section{{\faFlask} Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{Toxic Online Comments} {
   Toxicity classification in Wikipedia Comments and Twitter datasets by applying deep learning and transfer learning. Analyzed the results of sequential LSTM/GRU against state-of-the-art BERT models.}
   \resumeSubItem{Chess Player Ratings} {
     Predicting the Elo rating of a chess player from the moves sequence. Efforts involved EDA and feature engineering using Pandas and Matplotlib; as well as modeling with Linear Regression and Random Forest.}
   \resumeSubItem{Relationship Extraction}{An attention based and its performance evaluation on the SemEval-2010 Task 8 dataset.}
  \resumeSubItem{Skip-gram based Word2Vec}
      {A Word2Vec implementation with cross entropy loss and noise contrastive estimation as the objective functions. Evaluation is done on the semantic task of word analogies.}
  \resumeSubItem{Physual(\textit{Capstone})}
      {A text to scene generation system for Physics word problems based on StanfordCore NLP, Java 3D and Blender Models.}
  \resumeSubItem{\href{https://github.com/amanpreet692/HandleBarsEmailTemplate}
    {Email Template Generator}}
    {Built on the handlebars framework, creates templates to send out reactive email alerts.}       \resumeSubItem{\href{https://bitbucket.org/APS692/udp-with-error-detection} {Reliable UDP}}
      {Server-Client Exchange with Checksum validation and re-transmission in case of corrupt data.}
  \resumeSubHeadingListEnd

%-----------PUBLICATION(S)-----------------
\section{{\aiGoogleScholar} Publication(s)}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{http://research.ijcaonline.org/volume116/number14/pxc3902766.pdf}	{Visualization of Mechanics Problems based on Natural Language Processing}}
      {Summarized the research efforts and results of the aforementioned Capstone Project. (\textit{International Journal of Computer Applications - April,2015})}
      
\resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{{\faGears} Technical Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{Languages}{Java, Python, Unix Shell Scripting, SQL, MATLAB}
 \resumeSubItem{Frameworks}{Spring, Spring-Boot, JUnit, Mockito, Tensorflow, NumPy, Scikit-Learn, Pandas, Keras, Matplotlib}
 \resumeSubItem{Databases}{Sybase ASE, MongoDB, MySQL}
 \resumeSubItem{CI Tools}{Gradle, Team City, Git, Bitbucket, Ant, Jenkins, YourKit}
 \resumeSubHeadingListEnd

\end{document}